Legacy Data Confounds Modern Genomics Studies

### 2019-07-05 PlottingScripts/ProcessPlotData.Rmd
updated figures

jpt_imp <- merge(jpt_imp, suspicious, 
                 by = c('Chr', 'Pos'), all.x = T)

jpt_imp$Pos <- as.numeric(as.character(jpt_imp$Pos))

@@

imputed_position <- jpt_imp$Pos
suspicious_position <- jpt_imp[which(jpt_imp$Adjusted_Log10p > 2),]$Pos

jpt_imp$closest <- unlist(lapply(imputed_position, function(x) suspicious_position[which.min(abs(suspicious_position - x))]))
jpt_imp$dist <- abs(jpt_imp$closest - jpt_imp$Pos)

@@

#plot distance from nearest suspicious variant 
Rsq <- 
  ggplot(jpt_imp_sub, 
       aes(x= dist_2, 
           y = Rsq_mean)) +
  geom_point() +
  labs(x = "Distance from nearest suspicious variant",
       y = "Rsq") +
  xlim(c(0,10000))

AvgCall <- 
  ggplot(jpt_imp_sub, 
       aes(x= dist_2, 
           y = AvgCall_mean)) +
  geom_point() +
  labs(x = "Distance from nearest suspicious variant",
       y = "Average Call") +
  xlim(c(0,10000))

@@

ggsave(paste0(figurePath,
              "Imputation_Distance_10s.jpg"),
       height = 9,
       width = 9)
```

>>>>

#jpt_imp <- merge(jpt_imp, suspicious, 
#                 by = c('Chr', 'Pos'), all.x = T)

jpt_imp$Pos <- as.numeric(as.character(jpt_imp$Pos))
jpt_imp$Chr <- as.numeric(as.character(jpt_imp$Chr))

@@

close_list <- data.frame()
for(chrom in seq(1,22)){
  print(chrom)

  imputed_position <- 
    jpt_imp %>% 
    filter(Chr == chrom) %>%
    select(Pos) %>%
    unlist()

  suspicious_position <- 
    suspicious %>% 
    filter(Chr == chrom) %>%
    select(Pos) %>%
    unlist()

  close <- 
  unlist(lapply(imputed_position, 
                function(x) suspicious_position[which.min(abs(suspicious_position - x))]))

  out <- data.frame("Pos" = imputed_position, 
                       "closest" = close)
  rownames(out) <- NULL

  close_list <- rbind(close_list, out)
}

close_list
```

jpt_imp$dist <- abs(close_list$closest - close_list$Pos)

@@

#plot distance from nearest suspicious variant 
Rsq <- 
  ggplot(jpt_imp_sub, 
       aes(x= dist_2, 
           y = Rsq_mean)) +
  geom_point() +
  labs(x = "Distance from nearest suspicious variant",
       y = "Rsq") +
  xlim(c(0,5000))

AvgCall <- 
  ggplot(jpt_imp_sub, 
       aes(x= dist_2, 
           y = AvgCall_mean)) +
  geom_point() +
  labs(x = "Distance from nearest suspicious variant",
       y = "Average Call") +
  xlim(c(0,5000))

@@

ggsave(paste0(figurePath,
              "Imputation_Distance_100s_gw.jpg"),
       height = 9,
       width = 9)
```
